DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/comparison.tex
Update multimodel data for TX2-GPU
Added results for 4Nx1C test. Added relevant data, removed old data, and
updated Figure 17.

The Intel UP board and Jetson TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the results suggest that the TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

>>>>

The Intel UP board and Jetson TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 30 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the results suggest that the TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.
